Embedded Program Search in Agda

### 2020-05-06 paper/paper.tex
big update

A problem with using isomorphism over dependent types is its
undecidability\cite{HoTT}. The field is currently studying certain decidable
subsets of the problem thus we opt to maximize flexibility by parameterizing our
methods over a provided decidable type equality. The problem of type-directed
program search then just becomes the act of running the decision procedure for
this equality over the coded-types in our module. Thus, a searchable universe
can be defined:

>>>>

A problem with using isomorphism over dependent types is its
undecidability\cite{HoTT}. The field is currently studying certain decidable
subsets of the problem, thus we opt to maximize flexibility by parameterizing
our methods over a provided decidable type equality. The problem of
type-directed program search then just becomes the act of running the decision
procedure for this equality over the coded types in our module. Thus, a
searchable universe can be defined:
